Stay in shape! Homework exam II

### 2016-04-04 geometricAlgorithms/homeworkExam/2/homeworkExam.tex
finished 3??

However we can put an expectation on $k_p$ by using theorom 7.3 of the book
\cite{book}. It says the number of edges is at most $3n-6$, an edge is a
division between neigbours so the expected amount of neigbours per point
is $3$. So the expected storage complexity is:

\[ O(3n) = O(n) \]
\subsection{Query time}

>>>>

However we can put an expectation on $k_p$ by using theorom 7.3 of the book
\cite{book}. It says the number of edges is at most $3n-6$, an edge is a
division between neigbours so the expected amount of neigbours per point
is $\frac{3n-6}{n} \approx 3$. So the storage complexity is:

\[ O(3n) = O(n) \]

Note that this is not an expected complexity because the theorom 7.3 puts
a hard upperbound on the amount of neigbours as long as $n\geq3$.
\subsection{Query time}
The original datastructure had an expected query time of the follwoing order:

\[O(log(n))\]

This was given. Now we will analyse if the extension will impact this
perormance. The substructure is a trapezoidal map which has an expected
query time of $O(log(k))$ where $k$ is the amount of neigbours for a
particular point. If we combine this with the existing structure
we get an expected query time of:

\[O(log(n) \cdot log(k)) \]
